Application of Huynh 2020 Interim Analysis methods to assessed stocks from the US South Atlantic

### 2022-03-29 RunMSE/SEFSC/MSEPlots.Rmd
newest runs

library(Hmisc)
library(knitr)
library(latex2exp) # lets you use TeX() function to convert latex equations to R expressions for plotting
library(SAMtool)
library(stringr)
library(bamExtras)

@@

OMNames_user <- c("OM_BlackSeaBass",
                  "OM_VermilionSnapper",
                  "OM_RedPorgy",
                   #"OM_Tilefish","OM_Cobia",
                  "OM_SnowyGrouper"#,
                  #"OM_GagGrouper")#,
                   #"OM_capelin", "OM_POP", "OM_vs"
                   )
OMNames_huynh <- c("OM_CapelinHuynh", "OM_PacificOceanPerchHuynh", "OM_VermilionSnapperHuynh")

scenNames_user1 <-  c("base","dep","lf","epiM","ubias","tachi","rc")
scenNames_user2 <-  c("base","nolag","minerr","minrecdev","perfobs","ucvhi","ucvlo","vtiv"
                        )

# All scenarios
scenNames_user <- unique(c(scenNames_user1,scenNames_user2))

# Alternative realities
# These scenarios are considered equally plausible, for the purposes of
# averaging results together. Most other scenarios could be considered sensitivities.
scenNames_user_alt <- c("base","dep","lf","epiM","ubias","tachi","rc")

scenNames_key <- c("base"="Base",
                   "nolag"="No data lag",
                   "hs"="Hyper-stable","hd"="Hyper-deplete",
                   "dep"="Depleted","lf"="Lightly fished","epiM"="Episodic M",
                   "rc"="Regime\nchange", "ubias"="Index\nbiased","ucvhi"="Index\nHigh CV",
                   "ucvlo"="Index\nLow CV",
                   "perfobs"="Perfect observation",
                   "minerr"="Minimal error",
                   "minrecdev"="Minimal rec devs",
                   "tachi"="TAC 1.25MSY",
                   "vtiv"="V time invariant"
                   )

MPNamesAll <-         c(#"AvC",
                        "CC1",
                        #"DCAC","DBSRA","SPMSY",
                        "SCA_1","SCA_5","SCA_10",
                        "iMP_avg_5","iMP_avg_10",
                        "iMP_buffer_5","iMP_buffer_10",
                        "pMP_5","pMP_10"
                        )

MPNamesAll_key <- c("AvC"="average catch",
                    "CC1"="average catch (last 5 yr)",
                    "DCAC"= "depletion corrected average catch",
                    "DBSRA" = "depletion based stock reduction analysis",
                    "SPMSY" = "surplus production model",
                    "SCA_1" = "SCA 1 yr",
                    "SCA_5" = "SCA 5 yr",
                    "SCA_10"= "SCA 10 yr",
                    "iMP_avg_5" = "avg. index (5 yr)",
                    "iMP_avg_10" = "avg. index (10 yr)",
                    "iMP_buffer_5" = "buffer index (5 yr)",
                    "iMP_buffer_10" = "buffer index (10 yr)",
                    "pMP_5" = "projection (5 yr)",
                    "pMP_10" = "projection (10 yr)"
                        )
MPNamesAll_legtext <- MPNamesAll

MPNamesSub_user <- c("SCA_10","SCA_5","SCA_1","iMP_avg_10"#,"iMP_buffer_10"
                     )
MPNamesSub_user_legtext <- c("Fixed TAC (10)","Fixed TAC (5)","Annual assessment","Averaged Index (10)"#,"Buffered Index (10)"
                             )

# OMNames_user <- c("OM_BlackSeaBass","OM_SnowyGrouper","OM_VermilionSnapper")
# OMNames_user <- c("OM_RedPorgy","OM_Tilefish","OM_Cobia")
```

@@

plot_MSE_ts <- function(
myvarName="SSB",
myvarDenomExpr = NULL,
ylabel = myvarName,
FUN = mean,
scenNames,
OMNames,
MPNamesSub = NULL,
MPNamesSub_legtext=MPNamesSub,
MPNamesRef = NULL, # Name of reference MP
FUNRef = function(myvarsubStat,MPNamesRef){ # Function for comparing MPs with reference MP
  (myvarsubStat-myvarsubStat[,MPNamesRef])/myvarsubStat[,MPNamesRef]},
legtext_o = NULL, # order for plotting legend text
MSEoutNames = paste0(rep(gsub("OM","MSE",OMNames),each=length(scenNames)),
                     "_",
                     rep(scenNames,length(OMNames))
                     ),
colLabs = str_replace_all(gsub("OM_","",OMNames),"(?<=[a-z])(?=[A-Z])"," "),
rowLabs = scenNames,
sims = NULL, # which simulation runs should be used to generate the plot when plot_type="sims"?
plot_type="huynh", # "huynh" plots time series by MP like in the Huynh et al paper
                   # "boot" plots times series of bootstrapped data  with bamExtras::plot_boot_vec
                   # "phase" plots phase plots of F/Fmsy versus SSB/SSBmsy
                   # "tradeoff" plots tradeoff plots by MP
                   # "addind" plot additional indices from AddInd
                   # "sims" plot time series for individual sim runs
proyear_phase=NULL,
PMx = Yield, # Performance metric function x (x-axis) for tradeoff plots)
PMy = P75, # Performance metric function y (y-axis) for tradeoff plots)
mar=c(1,1,1,1),
oma=c(6,4,3,3),
mgp=c(1.5,0.2,0),
cols = setNames(ROGBP_alpha(0.5)(length(MPNamesSub)),MPNamesSub),
ltys = setNames(rep(1,length(MPNamesSub)),MPNamesSub),
pchs = setNames(rep(16,length(MPNamesSub)),MPNamesSub),
lwds = setNames(rep(3,length(MPNamesSub)),MPNamesSub),
types = setNames(rep("l",length(MPNamesSub)),MPNamesSub),
xlabel = "Management year",
main_line = 1, # Line for main column labels
xlim = NULL,
ylim = NULL,
assessmentYears=NULL,
x.at = NULL,
y.at = NULL,
# leg.x=NULL,
# leg.y =NULL,
legend_panel=NULL,
legend_cex= 1,
legend_x="bottomleft",
legend_inset=c(0,-0.5),
label_axes="all", # "all" labels all panels, "leftbottom" labels y axes on the left and x axes on the bottom panels
hline=1 # values to pass into abline(h=hline)
){
if(is.null(legtext_o)){
  legtext_o <- seq_along(MPNamesSub)
}

@@

matplot(projYears_i#as.numeric(rownames(myvarsubStat))
        ,myvarsubStat,
        col=cols,lty=ltys,lwd=lwds,type=types,
        xaxt=xaxt_i,yaxt=yaxt_i,
        xlim=xlim,ylim=ylim,xlab="",ylab="")
#title(main=colLabsAll[i],line=1)

@@

      for(MP_j in MPNamesSub){
      j <- match(MP_j,MPNamesSub)
      myvarsub_j <- myvarsub[,j,]
      lty <- ltys[j]
      if(j==1){
      matplot(projYears_i,
              t(myvarsub_j), 
              col=cols,lty=lty,lwd=lwds,type=types,
              xaxt=xaxt_i,yaxt=yaxt_i,
              xlim=xlim,ylim=ylim,xlab="",ylab="")
      #title(main=colLabsAll[i],line=1)

@@

plot_boot_vec(myvarsub[,j,],
              col_lines = col_AddInd[j],
              add=ifelse(j!=1,TRUE,FALSE),
              xlim=xlim,ylim=ylim)

@@

if(is.null(proyear_phase)){
  proyear_phase <- out_i@proyears
}
Bstatus <- out_i@SB_SBMSY[,MPNamesSubix,proyear_phase]
Fstatus <- out_i@F_FMSY[,MPNamesSubix,proyear_phase]

matplot(Fstatus,Bstatus,
        col=cols,lty=ltys,lwd=lwds,pch=pchs,type=types,
        xaxt=xaxt_i,yaxt=yaxt_i,
        xlab="",ylab="",xlim=xlim,ylim=ylim
        )
points(apply(Fstatus,2,median),
       apply(Bstatus,2,median),pch=21,cex=3,lwd=2,col="black",bg=makeOpaque(cols))

@@

@@

PMx_out <- PMx(out_i)
PMy_out <- PMy(out_i)

plot(PMx_out@Mean[MPNamesSubix],PMy_out@Mean[MPNamesSubix],pch=16,col=cols,
     xaxt=xaxt_i,yaxt=yaxt_i,
     xlab="",ylab="",
     xlim=xlim,ylim=ylim
     )

@@

if(!is.null(hline)){
abline(h=hline)
}

@@

```{r function PMsummary}
# compute and plot summary statistics for Performance metrics
PMsummary <- function(PMName,OMNames=OMNames_user,scenNames,MPs=NULL,
                      slot_to_plot="Prob", # Can be either "Prob" or "Stat"
                      main_line=-1.5,
                      hline=1,hline_lty=1,
                      par_args=list(mfrow=c(length(OMNames),1), 
                                    mar=c(0,2,0,1), oma=c(6,2,1,0),
                                    mgp=c(0.8,0.2,0), tck=-0.01),
                      ...){
PM <- get(PMName)
dots <- list(...)
if(!"ylab"%in%names(dots)){
  dots$ylab <- PMName
}

@@

for (OMNames_i in OMNames){
Names_i <- gsub("^OM_","",OMNames_i)
MSEoutNames_i = paste0(rep(gsub("OM","MSE",OMNames_i),each=length(scenNames)),
                     "_",
                     rep(scenNames,length(OMNames_i))
                     )
    out_list_i <- list()
    for(MSEoutNames_ij in MSEoutNames_i){
      scenNames_j <- str_extract(MSEoutNames_ij,"[a-z]+$")
      MSEout_ij <- get(MSEoutNames_ij)
      PMout_ij <- PM(MSEout_ij)
        MPs_ij <- PMout_ij@MPs
        out_ij <- slot(PMout_ij,slot_to_plot)
      if(!is.null(MPs)){
        out_ij <- out_ij[,match(MPs,MPs_ij)]
        MPs_ij <- MPs
      }
      dimnames(out_ij) <- list("sim"=seq(1:dim(out_ij)[1]), "MPs"=MPs_ij)
      out_ij <- cbind("scen"=scenNames_j,as.data.frame(out_ij))
      out_list_i[[MSEoutNames_ij]] <- out_ij

    }
    # Combine scenario outputs into large data frame with scen column indicating scenario
      out_df_i <- do.call(rbind,out_list_i)
      out_list[[paste0("out_df_",Names_i,"_",PMName)]] <- out_df_i
    # Plot stuff
      dots$xaxt <- ifelse(match(OMNames_i,rev(OMNames))==1,"s","n")

      do.call(boxplot,c(list(out_df_i[,-1],main=""),dots))
      mtext(Names_i,side=3,line=main_line,outer=FALSE,font=2)
      abline(h=hline,lty=hline_lty)
    }

@@

```{r function MSEsummary}
# compute and plot summary statistics for Performance metrics
MSEsummary <- function(MSEslotName,OMNames=OMNames_user,scenNames,MPs=NULL,
                       main_line=-1.5,
                       hline=1,hline_lty=1,
                      par_args=list(mfrow=c(length(OMNames),1),
                                    mar=c(3,2,1,1), oma=c(1,2,0,0),
                                    mgp=c(0.8,0.2,0), tck=-0.01),
                      ...){
dots <- list(...)
if(!"ylab"%in%names(dots)){
  dots$ylab <- MSEslotName
}
out_list <- list()

@@

for (OMNames_i in OMNames){
  Names_i <- gsub("^OM_","",OMNames_i)
  MSEoutNames_i = paste0(rep(gsub("OM","MSE",OMNames_i),each=length(scenNames)),
                         "_",
                         rep(scenNames,length(OMNames_i))
  )
  slot_list_i <- list()
  for(MSEoutNames_ij in MSEoutNames_i){
    scenNames_j <- str_extract(MSEoutNames_ij,"[a-z]+$")
    MSEout_ij <- get(MSEoutNames_ij)
    if(!is.expression(MSEslotName)){
      slot_k <- slot(MSEout_ij,MSEslotName) %>% apply(2,as.numeric)
    }else{
      slot_k <- eval(MSEslotName) %>% apply(2,as.numeric)
    }
    slot_k <- slot(MSEout_ij,MSEslotName) %>% apply(2,as.numeric)
    MPs_ij <- MSEout_ij@MPs
    if(!is.null(MPs)){
      slot_k <- slot_k[,match(MPs,MPs_ij)]
      MPs_ij <- MPs
    }
    dimnames(slot_k) <- list(NULL, "MPs"=MPs_ij)
    slot_k <- cbind("scen"=scenNames_j,as.data.frame(slot_k))
    slot_list_i[[MSEoutNames_ij]] <- slot_k

  }
  # Combine scenario outputs into large data frame with scen column indicating scenario
  slot_df_i <- do.call(rbind,slot_list_i)
  out_list[[paste0("slot_df_",Names_i,"_",MSEslotName)]] <- slot_df_i

  # Plot stuff
  do.call(boxplot,c(list(slot_df_i[,-1],main=""),dots))
  mtext(Names_i,side=3,line=main_line,outer=FALSE,font=2)
  abline(h=hline,lty=hline_lty)
}

@@

# Read in data for modified operating models
for(file.i in list.files("OM_modified")){
  assign(gsub(".rds","",file.i),readRDS(file.path("OM_modified",file.i)))
}

@@

OM_nsim <- c()
for(OM_Name_i in OMNames){
  i <- which(OMNames==OM_Name_i)
  OM_i <- get(OM_Name_i)
  nsim_i <- OM_i@nsim
  OM_nsim <- c(OM_nsim,nsim_i)
}

nsim_text <- combine_words(unique(OM_nsim),and=" or ")

# Read in MSE results
MSE_res_names <- gsub(".rds","",list.files("MSE_obj"))
#MSE_res_names <- gsub(".rds","",list.files("MSE_obj")[grepl("OM_",list.files("MSE_obj"))])
for(file.i in list.files("MSE_obj")){
  out_i <- readRDS(file.path("MSE_obj",file.i))
  names(out_i@PPD) <- out_i@MPs
  assign(gsub(".rds","",file.i),readRDS(file.path("MSE_obj",file.i)))
}
```

@@

```{r plot AddInd, eval=TRUE}
# This code is set up to make each set of plots for each MP, but the indices are basically the same
if(plot_pdf){pdf("Figs/AddInd.pdf")}
for(MP_name_i in "SCA_5"){#MPNamesAll){
    # Ind
    # MSE_i <- get(MSE_name_j)
    plot_MSE_ts(
      OMNames= OMNames, scenNames="base",
      myvarName = expression(slot(out_i@PPD[[MP_name_i]],"AddInd")),
      plot_type = "addind",
      ylabel = "index of abundance",
      # FUN=mean_noNA,
      MPNamesSub = MP_name_i,
      # MPNamesSub_legtext=MPNamesSub_user_legtext,
      #rowLabs=scenNames_key["addind"],
      xlabel="year",
      oma=c(3,4,5,3),
      ylim=c(0,8),
      main_line = -1.5,
      hline=NA
    )
  #title(main=MP_name_i,outer=TRUE)
}
if(plot_pdf){dev.off()}
```

```{r plot sims proj base, eval=FALSE}
MPs_sim <- c("SCA_1","SCA_5","iMP_avg_10")
scen <- "base"

@@

figName_ij <- paste0("sims_",MSEoutName_i,"_",scen,".pdf")
if(plot_pdf){pdf(file.path("Figs",figName_ij))}
plot_MSE_sims(MSEOut_i,MPs=MPs_sim,type="proj",
              lwd=2,sims=sample(1,1:50),
              title_main = paste0(Name_i,", ",scen),
              varNames = c("Catch","TAC","FM","F_FMSY",#"recruit",
                           "SSB","SB_SBMSY"))
if(plot_pdf){dev.off()}
}

>>>>

library(Hmisc)
library(knitr)
library(latex2exp) # lets you use TeX() function to convert latex equations to R expressions for plotting
library(openMSE)
library(stringr)
library(bamExtras)
library(bamMSE)

@@

OMNames_user <- c("OM_BlackSeaBass",
                  "OM_VermilionSnapper",
                  "OM_RedPorgy",
                   #"OM_Tilefish","OM_Cobia",
                  "OM_SnowyGrouper"#,
                  #"OM_GagGrouper"
                   )
Names_user <- gsub("^OM_","",OMNames_user)

OMNames_huynh <- c("OM_CapelinHuynh", "OM_PacificOceanPerchHuynh", "OM_VermilionSnapperHuynh")

scenNames_user1 <-  c("base","dep","lf","ucvhi","ubias","ucvlo")
scenNames_user2 <-  c("base","rc","minerr","minrecdev","vtiv")
scenNames_user3 <-  c("base","noempind",
                      "nolag","perfobs","tachi")
scenNames_user4 <-  c("base","lhset","Mset","steepset","agevarM"#,"epiM"
                      )

# All scenarios
scenNames_user <- unique(c(scenNames_user1,scenNames_user2,scenNames_user3,scenNames_user4))

# Alternative realities
# These scenarios are considered equally plausible, for the purposes of
# averaging results together. Most other scenarios could be considered sensitivities.
# scenNames_user_alt <- scenNames_user1

scenNames_key <- c("agevarM"="Age-varying M",
                   "base"="Base",
                   "dep"="Depleted",
                   "epiM"="Episodic M",
                   "hd"="Hyper-deplete",
                   "hs"="Hyper-stable",
                   "lf"="Lightly fished",
                   "lhset"="Set M and steep",
                   "mconst"="M constant",
                   "minerr"="Minimal error",
                   "minrecac"="Minimal rec AC",
                   "minrecdev"="Minimal rec devs",
                   "Mset"="Set M",
                   "noempind"="No empirical indices",
                   "nolag"="No data lag",
                   "perfobs"="Perfect observation",
                   "rc"="Regime\nchange",
                   "steepset"="Set steepness",
                   "tachi"="TAC 1.25MSY",
                   "ubias"="Index\nbiased",
                   "ucvhi"="Index\nHigh CV",
                   "ucvlo"="Index\nLow CV",
                   "vtiv"="V time invariant"
                   )

MPNamesAll <-         c(#"AvC", "CC1", "DCAC","DBSRA","SPMSY",
                        "SCA_1","SCA_5","SCA_10",
                        "pMP_5","pMP_10",                        
                        "iMP_avg_5","iMP_avg_10",
                        "iMP_buffer_5","iMP_buffer_10"
                        )

MPNamesAll_key <- c("AvC"="average catch",
                    "CC1"="average catch (last 5 yr)",
                    "DCAC"= "depletion corrected average catch",
                    "DBSRA" = "depletion based stock reduction analysis",
                    "SPMSY" = "surplus production model",
                    "SCA_1" = "Annual assessment",
                    "SCA_5" = "Fixed TAC (5)",
                    "SCA_10"= "Fixed TAC (10)",
                    "iMP_avg_5" = "Avg. index (5)",
                    "iMP_avg_10" = "Avg. index (10)",
                    "iMP_buffer_5" = "Buffer index (5)",
                    "iMP_buffer_10" = "Buffer index (10)",
                    "pMP_5" = "Projection (5)",
                    "pMP_10" = "Projection (10)"
                        )
MPNamesAll_legtext <- MPNamesAll

MPNamesSub_user <- c("SCA_1","SCA_5","SCA_10","iMP_avg_10","iMP_buffer_10")
MPNamesSub_user_legtext <- MPNamesAll_key[MPNamesSub_user]
```

@@

plot_MSE_ts <- function(
myvarName="SSB",
myvarDenomExpr = NULL,
ylabel = myvarName,
FUN = mean,
scenNames,
OMNames,
MPNamesSub = NULL,
MPNamesSub_legtext=MPNamesSub,
MPNamesRef = NULL, # Name of reference MP
FUNRef = function(myvarsubStat,MPNamesRef){ # Function for comparing MPs with reference MP
  (myvarsubStat-myvarsubStat[,MPNamesRef])/myvarsubStat[,MPNamesRef]},
legtext_o = NULL, # order for plotting legend text
MSEoutNames = paste0(rep(gsub("OM","MSE",OMNames),each=length(scenNames)),
                     "_",
                     rep(scenNames,length(OMNames))
                     ),
colLabs = str_replace_all(gsub("OM_","",OMNames),"(?<=[a-z])(?=[A-Z])"," "),
rowLabs = scenNames,
sims = NULL, # which simulation runs should be used to generate the plot when plot_type="sims"?
plot_type="huynh", # "huynh" plots time series by MP like in the Huynh et al paper
                   # "boot" plots times series of bootstrapped data  with bamExtras::plot_boot_vec
                   # "phase" plots phase plots of F/Fmsy versus SSB/SSBmsy
                   # "tradeoff" plots tradeoff plots by MP
                   # "addind" plot additional indices from AddInd
                   # "sims" plot time series for individual sim runs
proyear_phase=NULL,
proyear_phase_FUNName="median",
PMx = Yield, # Performance metric function x (x-axis) for tradeoff plots)
PMy = P100, # Performance metric function y (y-axis) for tradeoff plots)
PMx_Yrs=-10, # Defaults to the last 10 years 
PMy_Yrs=-10, # Defaults to the last 10 years
mar=c(1,1,1,1),
oma=c(6,4,3,3),
mgp=c(1.5,0.2,0),
cols = setNames(ROGBP_alpha(0.5)(length(MPNamesSub)),MPNamesSub),
ltys = setNames(rep(1,length(MPNamesSub)),MPNamesSub),
pchs = setNames(rep(16,length(MPNamesSub)),MPNamesSub),
lwds = setNames(rep(3,length(MPNamesSub)),MPNamesSub),
types = setNames(rep("l",length(MPNamesSub)),MPNamesSub),
xlabel = "Management year",
main_line = 1, # Line for main column labels
xlim = NULL,
ylim = NULL,
assessmentYears=NULL,
x.at = NULL,
y.at = NULL,
# leg.x=NULL,
# leg.y =NULL,
legend_panel=NULL,
legend_cex= 1,
legend_x="bottomleft",
legend_inset=c(0,-0.5),
label_axes="all", # "all" labels all panels, "leftbottom" labels y axes on the left and x axes on the bottom panels
hline=NULL, # values to pass into abline(h=hline)
vline=NULL, # values to pass into abline(v=vline)
hline_lty=3,
vline_lty=3,
...
){
if(is.null(legtext_o)){
  legtext_o <- seq_along(MPNamesSub)
}

@@

matplot(projYears_i#as.numeric(rownames(myvarsubStat))
        ,myvarsubStat,
        col=cols,lty=ltys,lwd=lwds,type=types,
        xaxt=xaxt_i,yaxt=yaxt_i,
        xlim=xlim,ylim=ylim,xlab="",ylab="",...)
#title(main=colLabsAll[i],line=1)

@@

      for(MP_j in MPNamesSub){
      j <- match(MP_j,MPNamesSub)
      myvarsub_j <- myvarsub[,j,]
      lty <- ltys[j]
      if(j==1){
      matplot(projYears_i,
              t(myvarsub_j), 
              col=cols,lty=lty,lwd=lwds,type=types,
              xaxt=xaxt_i,yaxt=yaxt_i,
              xlim=xlim,ylim=ylim,xlab="",ylab="",...)
      #title(main=colLabsAll[i],line=1)

@@

plot_boot_vec(myvarsub[,j,],
              col_lines = col_AddInd[j],
              add=ifelse(j!=1,TRUE,FALSE),
              xlim=xlim,ylim=ylim,...)

@@

if(is.null(proyear_phase)){
  proyear_phase <- out_i@proyears
}
proyear_phase_FUN <- get(proyear_phase_FUNName)
Bstatus <- out_i@SB_SBMSY[,MPNamesSubix,proyear_phase,drop=FALSE] %>% apply(1:2,proyear_phase_FUN)
Fstatus <- out_i@F_FMSY[,MPNamesSubix,proyear_phase,drop=FALSE] %>% apply(1:2,proyear_phase_FUN)

matplot(Fstatus,Bstatus,
        col=cols,lty=ltys,lwd=lwds,pch=pchs,type=types,
        xaxt=xaxt_i,yaxt=yaxt_i,
        xlab="",ylab="",xlim=xlim,ylim=ylim,
        ...
        )
points(apply(Fstatus,2,median),
       apply(Bstatus,2,median),pch=21,cex=3,lwd=2,col="black",bg=makeOpaque(cols))

@@

if(i%in%topPanels&i%in%leftPanels){
  if(length(proyear_phase)>1){
    leg_text_phase <- paste0(proyear_phase_FUNName,"(proyears ",paste(range(proyear_phase),collapse="-"),")")
  }else{
    leg_text_phase <- paste0("proyear ",proyear_phase)
  }
  legend("topright",legend=leg_text_phase,bty="n",text.col="black",text.font = 2)
}

@@

PMx_out <- PMx(out_i,Yrs=PMx_Yrs)
PMy_out <- PMy(out_i,Yrs=PMy_Yrs)

plot(PMx_out@Mean[MPNamesSubix],PMy_out@Mean[MPNamesSubix],pch=16,col=cols,
     xaxt=xaxt_i,yaxt=yaxt_i,
     xlab="",ylab="",
     xlim=xlim,ylim=ylim,
     ...)

@@

if(!is.null(hline)){
abline(h=hline,lty=hline_lty)
}
if(!is.null(vline)){
abline(v=vline,lty=vline_lty)
}

@@

```{r function PMsummary}

## NEED TO MODIFY THIS SO IT GROUPS THE GROUPED BOXPLOTS VISUALLY
# compute and plot summary statistics for Performance metrics
PMsummary <- function(PMName,
                      OMNames = OMNames_user,
                      scenNames,
                      MPs = NULL,
                      xaxis_label = NULL,
                      xaxis_label_outer = "Management procedure",
                      slot_to_plot = "Prob", # Can be either "Prob" or "Stat"
                      main_line = -1.5,
                      hline = 1,
                      hline_lty = 1,
                      par_args = list(mfrow = c(length(OMNames),1), mar = c(0,2,0,1), 
                                      oma = c(3,2,1,0), mgp = c(0.8,0.2,0), tck = -0.01),
                      n_yr_groups = 1, # Number of groups to split years into
                      group_space = NULL,  # Additional spacing between groups of boxes
                      ...){
  PM <- get(PMName)
  dots <- list(...)
  if(!"ylab"%in%names(dots)){
    dots$ylab <- PMName
  }
  if(!"col"%in%names(dots)){
    colorFUN = colorRampPalette(c("lightblue","darkblue"))
    dots$col <-  colorFUN(n_yr_groups)
  }
  if(is.null(group_space)){
    group_space <- (n_yr_groups-1)*.75
  }

@@

  for (OMNames_i in OMNames){
    Names_i <- gsub("^OM_","",OMNames_i)
    MSEoutNames_i = paste0(rep(gsub("OM","MSE",OMNames_i),each=length(scenNames)),
                           "_",
                           rep(scenNames,length(OMNames_i))
    )
    out_list_i <- list()
    for(MSEoutNames_ij in MSEoutNames_i){
      scenNames_j <- str_extract(MSEoutNames_ij,"[a-z]+$")
      MSEout_ij <- get(MSEoutNames_ij)
      proyears_ij <- MSEout_ij@proyears
      yr_ij <- 1:proyears_ij
      breaks_ij <- round(seq(min(yr_ij),max(yr_ij),length=n_yr_groups+1))

      yr_groups_ij <- as.numeric(cut(yr_ij,breaks=breaks_ij,include.lowest = TRUE))

      for(k in 1:n_yr_groups){
        MSEoutNames_ijk <- paste(MSEoutNames_ij,sprintf("%02.0f",k),sep="_")  
        PMout_ijk <- PM(MSEout_ij,Yrs=range(yr_ij[yr_groups_ij==k]))
        MPs_ijk <- PMout_ijk@MPs
        out_ijk <- slot(PMout_ijk,slot_to_plot)
        if(!is.null(MPs)){ # Possibly subset MPs
          out_ijk <- out_ijk[,match(MPs,MPs_ijk)]
          MPs_ijk <- MPs
        }
        dimnames(out_ijk) <- list("sim"=seq(1:dim(out_ijk)[1]), "MPs"=MPs_ijk)
        out_ijk <- cbind("scen"=scenNames_j,"yr_group"=k,as.data.frame(out_ijk))
        out_list_i[[MSEoutNames_ijk]] <- out_ijk

      } # end n_yr_groups
    } 
    # Combine scenario outputs into large data frame with scen column indicating scenario
    out_df_i <- do.call(rbind,out_list_i)
    out_df_i <- reshape2::melt(data=out_df_i,id.vars=c("scen","yr_group"))
    out_list[[paste0("out_df_",Names_i,"_",PMName)]] <- out_df_i

    # Plot stuff
    dots$xaxt <- ifelse(match(OMNames_i,rev(OMNames))==1,"n","n")
    n_group <- length(unique(out_df_i$yr_group))
    n_variable <- length(unique(out_df_i$variable))

    group_space_add <- rep(1:n_variable,each=n_group)*group_space
    box_at <- 1:(n_group*n_variable)+group_space_add

    xaxis_label_at <- apply(matrix(box_at,nrow=n_group,ncol=n_variable),2,mean)

    do.call(boxplot,c(list(formula = value ~ yr_group + variable, data = out_df_i,
                           main = "", at = box_at),dots))

    mtext(Names_i,side=3,line=main_line,outer=FALSE,font=2)
    abline(h=hline,lty=hline_lty)
  }
  if(is.null(xaxis_label)){xaxis_label <- MPs}

  axis(side = 1, at = xaxis_label_at, labels = xaxis_label)
  mtext(xaxis_label_outer,side=1,line=1.5, outer=TRUE,font=2)

@@

```{r function MSEsummary}
# compute and plot summary statistics for Performance metrics
MSEsummary <- function(MSEslotName,
                       OMNames=OMNames_user,
                       scenNames,
                       MPs=NULL,
                       xaxis_label = NULL,
                       xaxis_label_outer = "Management procedure",
                       main_line=-1.5,
                       hline=1,
                       hline_lty=1,
                      par_args=list(mfrow=c(length(OMNames),1), 
                                    mar=c(0,2,0,1), oma=c(3,2,1,0),
                                    mgp=c(0.8,0.2,0), tck=-0.01),
                      n_yr_groups=1, # Number of groups to split years into
                      FUN_yr_groups=NULL,
                      group_space = NULL,  # Additional spacing between groups of boxes
                      ...){
dots <- list(...)
if(!"ylab"%in%names(dots)){
  dots$ylab <- MSEslotName
}
if(!"col"%in%names(dots)){
 colorFUN = colorRampPalette(c("lightblue","darkblue"))
 dots$col <-  colorFUN(n_yr_groups)
}
if(is.null(group_space)){
  group_space <- (n_yr_groups-1)*.75
}

@@

for (OMNames_i in OMNames){
  Names_i <- gsub("^OM_","",OMNames_i)
  MSEoutNames_i = paste0(rep(gsub("OM","MSE",OMNames_i),each=length(scenNames)),
                         "_",
                         rep(scenNames,length(OMNames_i))
  )
  slot_list_i <- list()
  for(MSEoutNames_ij in MSEoutNames_i){
    scenNames_j <- str_extract(MSEoutNames_ij,"[a-z]+$")
    MSEout_ij <- get(MSEoutNames_ij)
    MPs_ij <- MSEout_ij@MPs
    proyears_ij <- MSEout_ij@proyears
    yr_ij <- 1:proyears_ij
    breaks_ij <- round(seq(min(yr_ij),max(yr_ij),length=n_yr_groups+1))

    yr_groups_ij <- as.numeric(cut(yr_ij,breaks=breaks_ij,include.lowest = TRUE))

    if(!is.expression(MSEslotName)){
      slot_k <- slot(MSEout_ij,MSEslotName)
    }else{
      slot_k <- eval(MSEslotName)
    }
    list_slot_km <- list()
    for(m in 1:n_yr_groups){
      if(is.null(FUN_yr_groups)){
      slot_km <- slot_k[,,which(yr_groups_ij==m)] %>% apply(2,as.numeric)
      }else{
      slot_km <- slot_k[,,which(yr_groups_ij==m)] %>% apply(1:2,FUN_yr_groups)
      }
    if(!is.null(MPs)){
      slot_km <- slot_km[,match(MPs,MPs_ij)]
      MPs_ij <- MPs
    }
      dimnames(slot_km) <- list(NULL, "MPs"=MPs_ij)
      list_slot_km[[m]] <- cbind("yr_group"=m,as.data.frame(slot_km))
    }

    slot_df_km <- do.call(rbind,list_slot_km)

    slot_df_km <- cbind("scen"=scenNames_j,as.data.frame(slot_df_km))
    slot_list_i[[MSEoutNames_ij]] <- slot_df_km

  }
  # Combine scenario outputs into large data frame with scen column indicating scenario
  slot_df_i <- do.call(rbind,slot_list_i)
  slot_df_i <- reshape2::melt(data=slot_df_i,id.vars=c("scen","yr_group"))
  out_list[[paste0("slot_df_",Names_i,"_",MSEslotName)]] <- slot_df_i

  # Plot stuff
  dots$xaxt <- ifelse(match(OMNames_i,rev(OMNames))==1,"n","n")
  n_group <- length(unique(slot_df_i$yr_group))
  n_variable <- length(unique(slot_df_i$variable))

  group_space_add <- rep(1:n_variable,each=n_group)*group_space
  box_at <- 1:(n_group*n_variable)+group_space_add

  xaxis_label_at <- apply(matrix(box_at,nrow=n_group,ncol=n_variable),2,mean)

  do.call(boxplot,c(list(formula=value~yr_group+variable,data=slot_df_i,main="",at=box_at),dots))
  mtext(Names_i,side=3,line=main_line,outer=FALSE,font=2)
  abline(h=hline,lty=hline_lty)
}
  if(is.null(xaxis_label)){xaxis_label <- MPs}

  axis(side = 1, at = xaxis_label_at, labels = xaxis_label)
  mtext(xaxis_label_outer,side=1,line=1.5, outer=TRUE,font=2)

@@

# Read in data for modified operating models
# for(file.i in list.files("OM_modified")){
#   assign(gsub(".rds","",file.i),readRDS(file.path("OM_modified",file.i)))
# }

@@

# Read in MSE results
MSE_res_names <- gsub(".rds","",list.files("MSE_obj"))
#MSE_res_names <- gsub(".rds","",list.files("MSE_obj")[grepl("OM_",list.files("MSE_obj"))])
for(file.i in list.files("MSE_obj")){
  if(file.i%in%paste0("MSE_",rep(Names_user,each=length(scenNames_user)),"_",scenNames_user,".rds")){

    out_i <- readRDS(file.path("MSE_obj",file.i))
    names(out_i@PPD) <- out_i@MPs
    assign(gsub(".rds","",file.i),readRDS(file.path("MSE_obj",file.i)))
    rm(out_i)
  }
}
```

@@

```{r plot AddInd, eval=TRUE}
# This code is set up to make each set of plots for each MP, but the indices are basically the same
if(plot_pdf){pdf("Figs/AddInd.pdf")}
for(MP_name_i in "SCA_10"){#MPNamesAll){
    # Ind
    # MSE_i <- get(MSE_name_j)
    plot_MSE_ts(
      OMNames= OMNames, scenNames="base",
      myvarName = expression(slot(out_i@PPD[[MP_name_i]],"AddInd")),
      plot_type = "addind",
      ylabel = "index of abundance",
      # FUN=mean_noNA,
      MPNamesSub = MP_name_i,
      # MPNamesSub_legtext=MPNamesSub_user_legtext,
      #rowLabs=scenNames_key["addind"],
      xlabel="year",
      oma=c(3,4,5,3),
      ylim=c(0,8),
      main_line = -1.5,
      hline=NA
    )
  #title(main=MP_name_i,outer=TRUE)
}
if(plot_pdf){dev.off()}
```

```{r plot sims proj base, eval=FALSE}
MPs_sim <- c("SCA_1","SCA_10","iMP_avg_10")
scen <- "base"

@@

figName_ij <- paste0("sims",gsub("MSE|_","",MSEoutName_i),".pdf")
if(plot_pdf){pdf(file.path("Figs",figName_ij))}
plot_MSE_sims(MSEOut_i,MPs=MPs_sim,type="proj",
              lwd=2,sims=sample(1,1:50),
              title_main = paste0(Name_i,", ",scen),
              varNames = c("Catch","TAC","FM","F_FMSY",#"recruit",
                           "SSB","SB_SBMSY"))
if(plot_pdf){dev.off()}
}
